Democracy, Public Support, and Measurement Uncertainty

### 2021-07-24 paper/dcpo_demsupport.Rmd
update moc models with expanded and corrected data.

#load(here("data", "pure_cls_ajps.rda")) 
#load(here("data", "pure_cls_apsr.rda")) 
load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
load(here("data", "exp_cls_ajps.rda"))
load(here("data", "exp_cls_apsr.rda"))

@@

mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
  exp_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expAJPS.RDS"))

@@

#df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  exp_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

@@

df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
  exp_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

@@

saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))

>>>>

#load(here("data", "pure_cls_ajps.rda")) 
#load(here("data", "pure_cls_apsr.rda")) 
load(here("data", "correct_cls_ajps.rda"))
load(here("data", "correct_cls_apsr.rda")) 
#load(here("data", "exp_cls_ajps.rda"))
#load(here("data", "exp_cls_apsr.rda")) 
load(here("data", "expcor_cls_ajps.rda"))
load(here("data", "expcor_cls_apsr.rda"))

@@

#mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_correctAJPS <- readRDS(here("output", "estimates_moc_correctAJPS.RDS")) 
#mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expcorAJPS.RDS"))
#mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_correctAPSR <- readRDS(here("output", "estimates_moc_correctAPSR.RDS"))
#mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expcorAPSR.RDS"))

@@

df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
  expcor_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

@@

saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expcorAJPS.RDS"))

@@

#df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
#  expcor_cls_apsr[[anEntry]] %>% 
#    plm::pdata.frame(index = c("country", "year"))
#}
#)

@@

df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
  expcor_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

@@

saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expcorAPSR.RDS"))
